Interval Probability for Fuzzy Quantum Theories

### 2016-05-12 prob.tex

\begin{definition}[Projection Operators; Orthogonality
~\cite{10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, an event is an \emph{elementary quantum
  test}~\cite{peres1995quantum}, which mathematically is represented
as a projection operator $P:\Hilb\rightarrow\Hilb$ onto a linear
subspace~$S$ of $\Hilb$. The set of all events can be defined
recursively as follow: \footnote {``Projection'' is sometimes called
  ``orthogonal projection" or ``self-adjoint projection" to emphasize
  $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}

>>>>

\begin{definition}[Projection Operators; Orthogonality~\cite{BirkhoffVonNeumann1936,10.2307/2308516,Redhead1987-REDINA,peres1995quantum,Swart2013}]
Given a Hilbert space $\Hilb$, an event\footnote{An event is formally called an experimental proposition~\cite{BirkhoffVonNeumann1936},
a question~\cite{10.2307/2308516}, or an elementary quantum test~\cite{peres1995quantum}} mathematically is represented as a projection operator
$P:\Hilb\rightarrow\Hilb$ onto a linear subspace~$S$ of $\Hilb$. The set of all
events can be defined recursively as follow:
\footnote {``Projection'' is sometimes called
``orthogonal projection" or ``self-adjoint projection" to
emphasize $P^{\dagger} = P$~\cite{Maassen2010}.}
\begin{itemize}
\item $\mathbb{0}$ is a projection.
\item For any vector $\ket{\psi}\in \Hilb$,
  $\frac{\proj{\psi}}{\ip{\psi}{\psi}}$ is a projection.
\item Projection operators $P_1$ and $P_2$ are orthogonal if $P_1P_2 =
  P_2P_1 = \mathbb{0}$. The sum of two orthogonal projections~$P_1 +
  P_2$ is also a projection. Moreover, if $P_1$ and $P_2$ project onto
  subspaces $S_1$ and $S_2$ respectively, then $P_1 + P_2$ will project onto the
  linear span of $S_1$ and $S_2$, i.e., $\left\{\ket{\psi_1} + \ket{\psi_2}
  \middle| \ket{\psi_1}\in S_1 \textrm{ and } \ket{\psi_2}\in S_2 \right\}$.
\end{itemize}
\end{definition}
